%% MQ-04-story.tex
\chapter{Story}

The manual reads:

\begin{quote}

For centuries the Focus Tower has stood at the very heart of the World. It had been a center for trade and knowledge, and the people of the World had met there to peacefully settle their differences. But on one warm summer day, the Tower was suddenly transformed into a symbol of the purest evil. For on that day, powerful monsters battled their way into the Tower, stole the four Crystals of the Earth, and then took off with the magical Coins that had kept the Tower’s doors unlocked.

With the Tower doors sealed behind them, the monsters relaxed their guard and turned their attention to the Crystals. As they basked in the radiant glow of the Crystals, the monsters grew stronger and meaner and even more wicked. The more light the monsters consumed, the more the World was drained of its warmth and color. Tremors soon shoock the land. The sky grew cloudy and dark. The seasons went berserk. Monsters appeared everywhere and terrorized the people. The World was thrown into total chaos. Something had to be done…
 
Enter Benjamin. Benjamin was the most normal youngster you would imagine. Like most responsible villagers his age, he arose at the crack of dawn to take his family’s livestock to the upper meadow to graze. Other kids teased him because he read while tending his heard, and because a village Elder had taken him in as a promising student. Although Benjamin seemed mature beyond his years, he still dreamed of being more than he was - faster, stronger and more daring. Little did he know his wishes were about to be fulfilled the hard way...

\end{quote}

In the opening cutscene, earthquakes have destroyed the hero’s home village. He just made it to the Hill of Destiny where he meets the old man for the first time, revealing to him that he is the Knight foretold by an old prophecy. Doubtful, the hero questions the old man’s motivation. But, before they can settle the argument they are attacked by a Behemoth. After the tutorial fight is over, the mountain is about to crumble. The old man flies off to the Level Forest and the hero hurriedly leaves the place with the same destination...

\bigskip

Only the North American manual mentions that the hero is called \textit{Benjamin}. Which does not matter too much, as the player can enter any name at the beginning of the game.
