%% MQ-12-05-01-focus_tower
\subsection{Focus Tower}
\label{map:focus_tower}

During most of the game you will use the \textit{Focus Tower} simply as a hub that connects the other regions of the world.

Note that there is a shortcut to the left in the cave under the tower from the \textit{Foresta} region leading to the main floor of the tower.

On the main floor there are four doors. The yellow door leads to the \textit{Aquaria} region. You first have to find the \nameref{item:sand_coin} in the \nameref{map:bone_dungeon} before you can open it. The stairs lead to a red chest with \nameref{spell:fire} on floor 2F.

The upper entrance from the \textit{Aquaria} region does not connect to any other exit. But it allows you to get the red chests with \nameref{spell:blizzard} and the \nameref{armor:venus_shield} on floor 2F. Only this way you can solve the jumping puzzle to access the \textit{Fireburg} region.

Once you have the \nameref{item:river_coin} you can open the blue door and go to the \textit{Fireburg} region.

The \nameref{item:sun_coin} is required to open the purple door that leads to the \textit{Windia} region. It also opens the way to the red chest on 2B containing \nameref{spell:aero}.

Finally the lake entrance eventually leads to the green door that can be opened with the \nameref{item:sky_coin}. It leads to the \nameref{map:doom_castle}. You must make your way to the center of the floor before you can procede. That is a bit tricky as the floor scrolls downwards. On the way pick up the \nameref{armor:aegis_shield}. Then fight \nameref{monster:skullrus_rex}.


\noindent\begin{tabularx}{\textwidth}[l]{lX}
	Monster & Group
\\ \hline
	\nameref{monster:minotaur_zombie}
	& \nameref{monster:minotaur_zombie}, \nameref{monster:shadow}, \nameref{monster:iflyte} \\
	& \nameref{monster:minotaur_zombie}, \nameref{monster:shadow}, \nameref{monster:chimera}
\\ \hline
	\nameref{monster:shadow}
	& \nameref{monster:shadow}, \nameref{monster:shadow} \\
	& \nameref{monster:shadow}, \nameref{monster:shadow}, \nameref{monster:shadow}
\\ \hline
	\nameref{monster:gorgon}
	& \nameref{monster:gorgon}, \nameref{monster:shadow}, \nameref{monster:phanquid} \\
	& \nameref{monster:gorgon}, \nameref{monster:shadow}, \nameref{monster:stheno}
\\ \hline
	Boss & \nameref{monster:skullrus_rex}
\\ \hline
	Items \\
	1F & Brown chest with \nameref{weapon:bomb}s \\
	2F & Red chest with \nameref{spell:fire} \\
	2F & Red chest with \nameref{armor:venus_shield} \\
	2F & Red chest with \nameref{spell:blizzard} \\
	3F & Brown chest with \nameref{item:cure_potion}s \\
	2B & Red chest with \nameref{spell:aero} \\
	2B & Red chest with \nameref{armor:aegis_shield}
\end{tabularx}
