%% MQ-12-03-11-lava_dome
\subsection{Lava Dome}
\label{map:lava_dome}

To open the large doors to the boss you have to step on the pressure plate in the lower right corner of the screen. Go down one ledge to the left and enter the cavern. Follow the wall to the right into another cave until you're back on the main screen. Stand on the pressure plate to the left.

Go back onto the second ledge and drop drown one level. Enter the cave here. Navigate the three caves until you exist on the other side of the main screen. Head left and up to enter another cave. Leave the second cave through the southeastern exit. Enter the final room.

Once you defeat \nameref{monster:dualhead_hydra} the earthquakes in the region stop and a shortcut back to the Aquaria region opens. With the \nameref{item:sun_coin} from the chest here, you can open yet another door in the \nameref{map:focus_tower}.


\noindent\begin{tabularx}{\textwidth}[l]{lX}
	Monster & Group
\\ \hline
	\nameref{monster:hotwings}
	& \nameref{monster:hotwings}, \nameref{monster:hotwings} \\
	& \nameref{monster:hotwings}, \nameref{monster:hotwings}, \nameref{monster:ninja} \\
	& \nameref{monster:hotwings}, \nameref{monster:hotwings}, \nameref{monster:hotwings}
\\ \hline
	\nameref{monster:ninja}
	& \nameref{monster:ninja}, \nameref{monster:ninja} \\
	& \nameref{monster:ninja}, \nameref{monster:ninja}, \nameref{monster:hotwings} \\
	& \nameref{monster:ninja}, \nameref{monster:ninja}, \nameref{monster:ninja}
\\ \hline
	\nameref{monster:stheno}
	& \nameref{monster:stheno} \\
	& \nameref{monster:stheno}, \nameref{monster:avizzard} \\
	& \nameref{monster:stheno}, \nameref{monster:avizzard}, \nameref{monster:ninja}
\\ \hline
	\nameref{monster:avizzard}
	& \nameref{monster:avizzard}, \nameref{monster:avizzard} \\
	& \nameref{monster:avizzard}, \nameref{monster:avizzard}, \nameref{monster:ninja} \\
	& \nameref{monster:avizzard}, \nameref{monster:avizzard}, \nameref{monster:avizzard}
\\ \hline
	\nameref{monster:fangpire}
	& \nameref{monster:fangpire}, \nameref{monster:fangpire} \\
	& \nameref{monster:fangpire}, \nameref{monster:fangpire}, \nameref{monster:avizzard} \\
	& \nameref{monster:fangpire}, \nameref{monster:fangpire}, \nameref{monster:fangpire}
\\ \hline
	\nameref{monster:adamant_turtle}
	& \nameref{monster:adamant_turtle}, \nameref{monster:adamant_turtle} \\
	& \nameref{monster:adamant_turtle}, \nameref{monster:adamant_turtle}, \nameref{monster:fangpire} \\
	& \nameref{monster:adamant_turtle}, \nameref{monster:adamant_turtle}, \nameref{monster:adamant_turtle}
\\ \hline
	\nameref{monster:iflyte}
	& \nameref{monster:iflyte} \\
	& \nameref{monster:iflyte}, \nameref{monster:fangpire} \\
	& \nameref{monster:iflyte}, \nameref{monster:fangpire}, \nameref{monster:fangpire}
\\ \hline
	\nameref{monster:salamand}
	& \nameref{monster:salamand}, \nameref{monster:salamand} \\
	& \nameref{monster:salamand}, \nameref{monster:salamand}, \nameref{monster:adamant_turtle} \\
	& \nameref{monster:salamand}, \nameref{monster:salamand}, \nameref{monster:salamand}
\\ \hline
	Boss & \nameref{monster:dualhead_hydra}
\\ \hline
	Items
	& Red chest with \nameref{armor:moon_helm} \\
	& Red chest with \nameref{spell:life} \\
	& Red chest with \nameref{item:sun_coin} \\
	& Brown chests with \nameref{item:cure_potion}s \\
	& Brown chests with \nameref{item:heal_potion}s \\
	& Brown chests with \nameref{weapon:bomb}s \\
	& Brown chests with \nameref{item:refresher}s
\end{tabularx}
