%% MQ-12-04-13-macs_ship
\subsection{Mac's Ship}
\label{map:macs_ship}

Remember that you can push barrels and jump over them. You can also climb the mast and large robe. Look out for squares with a black cross. They will crumble when you step onto them; you will end up one floor below.

Once you reach \nameref{char:mac}, the ship is cleared of all monsters. \nameref{char:kaeli} takes her father to the inn of \nameref{map:windia} to treat his wounds. When you leave the ship to follow her, \nameref{char:spencer} and \nameref{char:tristam} appear telling you that \nameref{char:phoebe} is waiting for you in \nameref{map:windia}.

At the inn \nameref{char:phoebe} joins you. Talk to \nameref{char:mac} upstairs then take his ship to yet another entrance of the \nameref{map:focus_tower}.

\bigskip

When you use the ship to sail to the waterfront entrance of the \nameref{map:focus_tower}, you'll find traders underdeck that sell \nameref{item:seed}s and \nameref{item:cure_potion}s. The brown chests remain and restock.


\noindent\begin{tabularx}{\textwidth}[l]{lX}
	Monster & Group
\\ \hline
	\nameref{monster:naga}
	& \nameref{monster:naga}, \nameref{monster:naga} \\
	& \nameref{monster:naga}, \nameref{monster:naga}, \nameref{monster:naga}
\\ \hline
	\nameref{monster:thanatos}
	& \nameref{monster:thanatos}, \nameref{monster:thanatos} \\
	& \nameref{monster:thanatos}, \nameref{monster:manticor}, \nameref{monster:beholder}
\\ \hline
	\nameref{monster:gargoyle}
	& \nameref{monster:gargoyle}, \nameref{monster:gargoyle} \\
	& \nameref{monster:gargoyle}, \nameref{monster:gargoyle}, \nameref{monster:gargoyle}
\\ \hline
	\nameref{monster:chimera}
	& \nameref{monster:chimera} \\
	& \nameref{monster:chimera}, \nameref{monster:sorcerer} \\
	& \nameref{monster:chimera}, \nameref{monster:sorcerer}, \nameref{monster:sorcerer}
\\ \hline
	Items
	& Red chest with \nameref{armor:aegis_shield} \\
	& Brown chests with \nameref{item:cure_potion}s \\
	& Brown chests with \nameref{item:heal_potion}s \\
	& Brown chest with \nameref{item:refresher}s \\
	& Brown chests with \nameref{weapon:bomb}s or \hyperref[weapon:bow_of_grace]{arrows}, depending on your companion
\end{tabularx}
