%% MQ-12-04-02-alive_forest
\subsection{Alive Forest}
\label{map:alive_forest}

The forest houses a \nameref{map:giant_tree}. When you reach it \nameref{char:tristam} suggests to go fetch \nameref{char:kaeli} from \nameref{map:aquaria}. \nameref{char:kaeli} is in \nameref{char:phiebe}'s house. But she's asleep. Go talk to \nameref{char:spencer} instead.

\nameref{char:spencer} cannot dig a tunnle far enough to reach \nameref{char:mac}'s ship. He needs the help of \nameref{char:otto} from \nameref{map:windia}. Meanwhile he goes treasure hunting and \nameref{char:tristam} joins him. Before they leave, \nameref{char:tristam} gives you his \nameref{weapon:dragon_claw}.

Since \nameref{char:spencer} is preoccupied, \nameref{char:phoebe} has the idea to use explosives which causes parts of the cave to collapse. She runs off and you can fetch \nameref{char:kaeli}. Make your way back to the \nameref{map:giant_tree}.

\bigskip

The tree stumps with teleport pads atop are hollow and contain brown chests. The corresponding pads are hidden under regular trees nearby. Look for small trees that stand alone.


\noindent\begin{tabularx}{\textwidth}[l]{lX}
	Monster & Group
\\ \hline
	\nameref{monster:mummy}
	& \nameref{monster:mummy}, \nameref{monster:mummy} \\
	& \nameref{monster:mummy}, \nameref{monster:mummy}, \nameref{monster:spector} \\
	& \nameref{monster:mummy}, \nameref{monster:mummy}, \nameref{monster:mummy}
\\ \hline
	\nameref{monster:spector}
	& \nameref{monster:spector}, \nameref{monster:spector} \\
	& \nameref{monster:spector}, \nameref{monster:spector}, \nameref{monster:mummy} \\
	& \nameref{monster:spector}, \nameref{monster:spector}, \nameref{monster:spector}
\\ \hline
	Items
	& Red chests with \nameref{weapon:giants_axe} \\
	& Brown chests with \nameref{item:cure_potion}s \\
	& Brown chest with \nameref{item:heal_potion}s \\
	& Brown chests with \nameref{item:refresher}s \\
	& Brown chest with \hyperref[weapon:bow_of_grace]{arrows}
\end{tabularx}
