%% MQ-12-04-10-pazuzus_tower
\subsection{Pazuzu's Tower}
\label{map:pazuzus_tower}

You will find \nameref{char:norma} just right of the entrance. She will return to \nameref{map:windia} once you talk to her.

The tower has an annoying layout. First you climb the odd floors before you can descend to the even ones. It can be difficult to see ledges and gaps you can jump over. 

In theory you may only have to flick one switch to stop \nameref{monster:pazuzu} escaping. But you also have to make your way back to where he is at the moment. Therefore, it is most likely that you first switch all levers and then fight him.

Once he's down, the elevator takes you to the top of the tower. There the air crystal is freed and you can take the \nameref{item:sky_coin} from the red chest. That coin opens the final door in the \nameref{map:focus_tower}. But the way to that door needs to be found first.

Go back to \nameref{map:windia} and speak to \nameref{char:otto}. He reminds you that \nameref{char:mac} is still stuck. Since \nameref{char:spencer}'s cave collapsed in \nameref{map:aquaria} you have to find another way. \nameref{char:otto} thinks about extending the rainbow bridge. But for that be needs the \nameref{item:thunder_rock}. \nameref{char:reuben} rejoins and together you make your way back to \nameref{map:fireburg} asking \nameref{char:arion} about the \nameref{item:thunder_rock}.

\nameref{char:arion} gives you the \nameref{item:thunder_rock} which opens up the way to \nameref{map:spencers_place}.


\noindent\begin{tabularx}{\textwidth}[l]{lX}
	Monster & Group
\\ \hline
	\nameref{monster:garuda}
	& \nameref{monster:garuda}, \nameref{monster:garuda} \\
	& \nameref{monster:garuda}, \nameref{monster:garuda}, \nameref{monster:gargoyle} \\
	& \nameref{monster:garuda}, \nameref{monster:garuda}, \nameref{monster:garuda}
\\ \hline
	\nameref{monster:beholder}
	& \nameref{monster:beholder}, \nameref{monster:beholder} \\
	& \nameref{monster:beholder}, \nameref{monster:beholder}, \nameref{monster:beholder}
\\ \hline
	\nameref{monster:manticor}
	& \nameref{monster:manticor}, \nameref{monster:manticor} \\
	& \nameref{monster:manticor}, \nameref{monster:manticor}, \nameref{monster:manticor}
\\ \hline
	\nameref{monster:chimera}
	& \nameref{monster:chimera} \\
	& \nameref{monster:chimera}, \nameref{monster:sorcerer} \\
	& \nameref{monster:chimera}, \nameref{monster:sorcerer}, \nameref{monster:sorcerer}
\\ \hline
	\nameref{monster:thanatos}
	& \nameref{monster:thanatos} \\
	& \nameref{monster:thanatos}, \nameref{monster:manticor} \\
	& \nameref{monster:thanatos}, \nameref{monster:manticor}, \nameref{monster:beholder}
\\ \hline
	\nameref{monster:sorcerer}
	& \nameref{monster:sorcerer} \\
	& \nameref{monster:sorcerer}, \nameref{monster:sorcerer} \\
	& \nameref{monster:sorcerer}, \nameref{monster:sorcerer}, \nameref{monster:beholder}
\\ \hline
	\nameref{monster:naga}
	& \nameref{monster:naga}, \nameref{monster:naga} \\
	& \nameref{monster:naga}, \nameref{monster:naga}, \nameref{monster:naga}
\\ \hline
	\nameref{monster:gargoyle}
	& \nameref{monster:gargoyle} \\
	& \nameref{monster:gargoyle}, \nameref{monster:gargoyle} \\
	& \nameref{monster:gargoyle}, \nameref{monster:gargoyle}, \nameref{monster:gargoyle}
\\ \hline
	Boss & \nameref{monster:pazuzu}
\\ \hline
	Items
	& Red chest with \nameref{weapon:excalibur} \\
	& Red chest with \nameref{spell:flare} \\
	& Brown chests with \nameref{item:cure_potion}s \\
	& Brown chests with \nameref{item:heal_potion}s \\
	& Brown chest with \nameref{item:refresher}s \\
	& Brown chests with \nameref{weapon:bomb}s
\end{tabularx}
